This is RMarkdown file for PeerAssigment_1 Reproduceable Research Course
=============================================================================

##Reading data

```{r}
RepData <- read.csv("activity.csv")
```

##What is mean total number of steps taken per day? 

###Processing Data
```{r}
steps <- tapply(RepData$steps, RepData$date, sum, na.rm = TRUE)
```

###Create Histogram
```{r}
hist(steps, breaks = 10)
```

###Calculate Mean and Median
```{r results='hide'}
steps_median <- median(steps)
steps_mean <- mean(steps)
```
Number of steps taken each day Median is `r steps_median`, and  Mean is `r steps_mean`.

##What is the average daily activity pattern?
###Processing Data
```{r}
steps_by_interval<-as.data.frame(tapply(RepData$steps,  RepData$interval, sum, na.rm = TRUE))
steps_by_interval$intreval <- row.names(steps_by_interval)
names(steps_by_interval) <- c("steps","intreval")
```

###Create Plot
```{r}
with(steps_by_interval, plot(intreval, steps, main = "Avarage number of steps by periods", 
             type="l", xlab="Interval", ylab="Steps"))
```

###Find period with maximum of steps

```{r results='hide'}
max_period <- steps_by_interval$intreval[which.max(steps_by_interval$steps)]
max_steps <- max(steps_by_interval$steps)
```
The Period with maximum of steps is `r max_period` and maximum value of steps is `r max_steps`

##Imputing missing values

###Calculating and reporting the total number of missing values in the dataset
```{r}
sum(is.na(RepData$steps))
```

###Strategy for filling in all of the missing values in the dataset
NA will be repaced by mean of current interval across all days

###Creating new dataset with replaced NA
```{r results='hide'}
steps_mean_by_interval<-as.data.frame(tapply(RepData$steps,  RepData$interval, mean, na.rm = TRUE))
steps_mean_by_interval$intreval <-as.integer(row.names(steps_mean_by_interval))
names(steps_mean_by_interval) <- c("steps","intreval")
NO_NA_RepData <- RepData
for (i in 1:nrow(RepData) ) {
  if (is.na(NO_NA_RepData[i, 1])) {
    NO_NA_RepData[i, 1] <- as.integer(steps_mean_by_interval$steps[which(steps_mean_by_interval$intreval == 15)])
   }
}

```
###Create Histogram
```{r}
steps_NA <- tapply( NO_NA_RepData$steps,  NO_NA_RepData$date, sum, na.rm = TRUE)
hist(steps_NA , breaks = 10)
```
Hist of the first part of Assigment looks a very similar as Hist of third part, so in my opinion NA has not strong influence on result of research.

##Differences in activity patterns between weekdays and weekends

###Creating a new factor variable in the dataset with two levels - "weekday" and "weekend"
```{r}
RepData$date<- as.Date(RepData$date)
weekdays_days <- c('Monday', 'Tuesday', 'Wednesday', 'Thursday', 'Friday')
RepData$wDay <- factor((weekdays(RepData$date) %in% weekdays_days), levels=c(FALSE, TRUE), labels=c('weekend', 'weekday'))
weekdays_day<-subset(RepData,RepData$wDay == 'weekday')
weekdays_end<-subset(RepData,RepData$wDay == 'weekend')
steps_by_interval_weeks<-as.data.frame(tapply(weekdays_day$steps, weekdays_day$interval, sum, na.rm = TRUE))

steps_by_interval_weeks$intreval <- row.names(steps_by_interval_weeks)


```